---
title: "Linear modeling"
output: html_notebook
---

This document breaks down the linear modeling to assess factors that seem to be important.

setup:

```{r}
source("utils.R")
raw_dataset <- get_raw_dataset()
```

```{r}

source("utils.R")

data_per_participant <- create_participant_data(raw_dataset)

```

# Descriptive stats

Graphs of stats taht we might wanna know for modeling below

```{r}
hist(data_per_participant$AgeGap[abs(data_per_participant$AgeGap)<30],breaks = -30:30)
```

Need to know if this is really valid thuogh--how many people in each group?
```{r}
# table(dts$`How do you currently keep your pubic hair?`, dts$Politics, dts$Gender3C)
```

```{r}
table(data_per_participant$`How do you currently keep your pubic hair?`, data_per_participant$Politics5L, data_per_participant$Gender3C)
```


#General gender breakdown
<!--```{r fig.width=6,fig.height=4.5}-->
```{r fig.width=20,fig.height=16}

dts<-data_per_participant #%>% filter(Gender3C %in% )
dts$Gender3C<-factor(dts$Gender3C,c("Female","Male"))
crosstabs <- table(dts$`How do you currently keep your pubic hair?`, dts$Politics5L, dts$Gender3C)/rep(table(dts$Politics5L,dts$Gender3C),each=4)
percents <- data.frame(
  crosstabs
)

print(crosstabs)

colnames(percents) <- c("Hair style","Politics","Gender3C","Percent")

percents$`Hair style`<-factor(percents$`Hair style`,levels=rev(levels(percents$`Hair style`)))
library(ggplot2)
library(ggthemes)
#install.packages("hrbrthemes") # NOTE: CRAN version is 0.8.0
library(hrbrthemes)
# devtools::install_github('datarootsio/artyfarty')
# library("artyfarty")
#https://towardsdatascience.com/themes-to-spice-up-visualizations-with-ggplot2-3e275038dafa

pattern_named_vec<-get_pattern_named_vec("image_key.csv","images/indpat5/")

percents$Labels <- as.character(percents$`Hair style`)
percents$Labels[percents$Percent<0.1]<-""
politics_labels_tidy<-function(charvec){stringr::str_replace_all(stringr::str_replace_all(charvec," or ", " / "),"-wing","")}
percents$Politics<-factor(politics_labels_tidy(as.character(percents$Politics)),levels= politics_labels_tidy(as.character(levels(percents$Politics))))

text_size <-25
ggplot_politics_base<-ggplot(percents, aes(fill=`Hair style`, x=Politics,y=Percent)) + 
  #geom_bar(position="fill", stat="identity")+
  geom_col_pattern(
    aes(fill=`Hair style`,pattern_filename=interaction(`Hair style`,Gender3C)),
    pattern = 'image', pattern_gravity = "center", pattern_type= 'none',pattern_scale = -2
    )+
  scale_pattern_filename_manual(values = pattern_named_vec) +
  guides(pattern_filename="none")+
  scale_y_continuous(labels=scales::percent_format())+
  scale_x_discrete(labels = function(x) str_wrap(x,width=15))+
  coord_flip()+
  #geom_text(aes(label = str_wrap(Labels,width=10)), hjust = 0,position = position_fill(vjust = 0)) +
  #theme_classic()+
  #theme_fivethirtyeight()+
  #facet_grid(Gender3C~.)+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",
        text = element_text(size = text_size,face = "bold",color="#bd0026"),
        legend.text = element_text(size=text_size),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=text_size),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(color="#000000",size=text_size)
        )+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Hair style by Gender")

#print(ggplot_politics_base+facet_grid(Gender3C~.))
  



```


```{r fig.width=40,fig.height=10}
print(ggplot_politics_base+facet_grid(.~Gender3C))
```

```{r fig.width=40,fig.height=10}
percents$PoliticsInt<-as.integer(percents$Politics)
#percents_max %>% select(PoliticsInt %in% c(max(PoliticsInt))
ggplot_politics_area_base<-ggplot(percents, aes(fill=`Hair style`, x=PoliticsInt,y=Percent)) + 
  geom_area_pattern(aes(fill=`Hair style`,pattern_filename=interaction(`Hair style`,Gender3C)),
    alpha=1.0,pattern = 'image', pattern_gravity = "center", pattern_type= 'none',pattern_scale = -2
    )+
  scale_pattern_filename_manual(values = pattern_named_vec) +
  guides(pattern_filename="none")+
  scale_y_continuous(labels=scales::percent_format())+
  #scale_x_discrete(labels = function(x) str_wrap(x,width=15))+
  scale_x_continuous(labels=levels(percents$Politics))+
  geom_vline(xintercept=(1:length(unique(percents$Politics))),color="#333333")+
  coord_flip()+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=18),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=18),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major  = element_blank(),
        panel.grid.minor = element_blank(),
        #panel.grid.minor.y = element_blank(),
        strip.text = element_text(color="#000000",size=18)
        )+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Hair style by Gender")

print(ggplot_politics_area_base+facet_grid(.~Gender3C))


```




```{r}
counts <- data.frame(
  table( dts$Politics5L)
)
counts
```


Women living or not living with their partner...

```{r}
dts<-data_per_participant %>% filter(Gender3C=="Female") #%>% filter(`Relationship type` %in% c("Committed relationship","Dating","Casual"))
table(dts$`How do you currently keep your pubic hair?`, dts$Politics4L, dts$MarriedOrLivingTogether)

```


```{r fig.width=20,fig.height=5}

percents <- data.frame(
  table(dts$`How do you currently keep your pubic hair?`, dts$Politics4L, dts$MarriedOrLivingTogether)/rep(table(dts$Politics4L,dts$MarriedOrLivingTogether),each=4)
)
colnames(percents) <- c("Hair style","Politics","MarriedOrLivingTogether","Percent")

library(ggplot2)
library(ggthemes)
#install.packages("hrbrthemes") # NOTE: CRAN version is 0.8.0
library(hrbrthemes)
# devtools::install_github('datarootsio/artyfarty')
# library("artyfarty")
#https://towardsdatascience.com/themes-to-spice-up-visualizations-with-ggplot2-3e275038dafa

percents$Labels <- as.character(percents$`Hair style`)
percents$Labels[percents$Percent<0.1]<-""
ggplot(percents, aes(fill=`Hair style`, x=Politics,y=Percent)) + 
  geom_bar(position="fill", stat="identity")+scale_y_continuous(labels=scales::percent_format())+
  coord_flip()+
  #geom_text(aes(label = str_wrap(Labels,width=10)), hjust = 0,position = position_fill(vjust = 0)) +
  #theme_classic()+
  #theme_fivethirtyeight()+
  facet_grid(~MarriedOrLivingTogether)+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=22),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=22),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
        )+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Hair style by Gender")



```


```{r fig.width=20,fig.height=5}
dts<-data_per_participant %>% filter(MarriedOrLivingTogether)
dts$Gender3C<-factor(dts$Gender3C,c("Male","Female"))
percents <- data.frame(
  table(dts$`How do you currently keep your pubic hair?`, dts$Politics4L, dts$Gender3C)/rep(table(dts$Politics4L,dts$Gender3C),each=4)
)
colnames(percents) <- c("Hair style","Politics","Gender3C","Percent")

library(ggplot2)
library(ggthemes)
#install.packages("hrbrthemes") # NOTE: CRAN version is 0.8.0
library(hrbrthemes)
# devtools::install_github('datarootsio/artyfarty')
# library("artyfarty")
#https://towardsdatascience.com/themes-to-spice-up-visualizations-with-ggplot2-3e275038dafa

percents$Labels <- as.character(percents$`Hair style`)
percents$Labels[percents$Percent<0.1]<-""
ggplot(percents, aes(fill=`Hair style`, x=Politics,y=Percent)) + 
  geom_bar(position="fill", stat="identity")+scale_y_continuous(labels=scales::percent_format())+
  coord_flip()+
  #geom_text(aes(label = str_wrap(Labels,width=10)), hjust = 0,position = position_fill(vjust = 0)) +
  #theme_classic()+
  #theme_fivethirtyeight()+
  facet_grid(~Gender3C)+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=22),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=22),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
        )+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Hair style by Gender",subtitle="Married or living together")



```



```{r fig.width=20,fig.height=5}
dts<-data_per_participant %>% filter(MarriedOrLivingTogether==FALSE)
dts$Gender3C<-factor(dts$Gender3C,c("Male","Female"))
percents <- data.frame(
  table(dts$`How do you currently keep your pubic hair?`, dts$Politics4L, dts$Gender3C)/rep(table(dts$Politics4L,dts$Gender3C),each=4)
)
colnames(percents) <- c("Hair style","Politics","Gender3C","Percent")

library(ggplot2)
library(ggthemes)
#install.packages("hrbrthemes") # NOTE: CRAN version is 0.8.0
library(hrbrthemes)
# devtools::install_github('datarootsio/artyfarty')
# library("artyfarty")
#https://towardsdatascience.com/themes-to-spice-up-visualizations-with-ggplot2-3e275038dafa

percents$Labels <- as.character(percents$`Hair style`)
percents$Labels[percents$Percent<0.1]<-""
ggplot(percents, aes(fill=`Hair style`, x=Politics,y=Percent)) + 
  geom_bar(position="fill", stat="identity")+scale_y_continuous(labels=scales::percent_format())+
  coord_flip()+
  #geom_text(aes(label = str_wrap(Labels,width=10)), hjust = 0,position = position_fill(vjust = 0)) +
  #theme_classic()+
  #theme_fivethirtyeight()+
  facet_grid(~Gender3C)+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=22),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=22),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
        )+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Hair style by Gender",subtitle="living separately or casual")



```




## Age




```{r fig.width=20,fig.height=5}

data_per_participant$AgeGroup<-floor((data_per_participant$Age+2)/5)*5-2
dts<-data_per_participant %>% filter(`Relationship type`=="Committed relationship" & Age<43)
dts$Gender3C<-factor(dts$Gender3C,c("Male","Female"))
percents <- data.frame(
  table(dts$`How do you currently keep your pubic hair?`, dts$AgeGroup, dts$Gender3C)/rep(table(dts$AgeGroup,dts$Gender3C),each=4)
)
colnames(percents) <- c("Hair style","AgeGroup","Gender3C","Percent")

library(ggplot2)
library(ggthemes)
#install.packages("hrbrthemes") # NOTE: CRAN version is 0.8.0
library(hrbrthemes)
# devtools::install_github('datarootsio/artyfarty')
# library("artyfarty")
#https://towardsdatascience.com/themes-to-spice-up-visualizations-with-ggplot2-3e275038dafa

percents$Labels <- as.character(percents$`Hair style`)
percents$Labels[percents$Percent<0.1]<-""
ggplot(percents, aes(fill=`Hair style`, x=AgeGroup,y=Percent)) + 
  geom_bar(position="fill", stat="identity")+scale_y_continuous(labels=scales::percent_format())+
  coord_flip()+
  #geom_text(aes(label = str_wrap(Labels,width=10)), hjust = 0,position = position_fill(vjust = 0)) +
  #theme_classic()+
  #theme_fivethirtyeight()+
  facet_grid(~Gender3C)+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=22),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=22),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
        )+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Hair style by Gender",subtitle="Age group (5 year brackets) for people in committed relationships living apart")



```


#By politics and Partner's politics...



```{r fig.width=20,fig.height=16}

dts<-data_per_participant #%>% filter(Gender3C %in% )
dts$Gender3C<-factor(dts$Gender3C,c("Female","Male"))

crosstabs <- table(dts$`How do you currently keep your pubic hair?`, dts$PartnerPolitics5L, dts$Gender3C)/rep(table(dts$PartnerPolitics5L,dts$Gender3C),each=4)
print(crosstabs)
percents <- data.frame(
  crosstabs
)


colnames(percents) <- c("Hair style","PartnerPolitics","Gender3C","Percent")


percents$`Hair style`<-factor(percents$`Hair style`,levels=rev(levels(percents$`Hair style`)))
library(ggplot2)
library(ggthemes)
#install.packages("hrbrthemes") # NOTE: CRAN version is 0.8.0
library(hrbrthemes)
# devtools::install_github('datarootsio/artyfarty')
# library("artyfarty")
#https://towardsdatascience.com/themes-to-spice-up-visualizations-with-ggplot2-3e275038dafa

percents$Labels <- as.character(percents$`Hair style`)
percents$Labels[percents$Percent<0.1]<-""
politics_labels_tidy<-function(charvec){stringr::str_replace_all(stringr::str_replace_all(charvec," or ", " / "),"-wing","")}
percents$PartnerPolitics<-factor(politics_labels_tidy(as.character(percents$PartnerPolitics)),levels= politics_labels_tidy(as.character(levels(percents$PartnerPolitics))))
ggplot(percents, aes(fill=`Hair style`, x=PartnerPolitics,y=Percent)) + 
  geom_bar(position="fill", stat="identity")+scale_y_continuous(labels=scales::percent_format())+
  scale_x_discrete(labels = function(x) str_wrap(x,width=15))+
  coord_flip()+
  #geom_text(aes(label = str_wrap(Labels,width=10)), hjust = 0,position = position_fill(vjust = 0)) +
  #theme_classic()+
  #theme_fivethirtyeight()+
  facet_grid(Gender3C~.)+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=18),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=18),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(color="#000000",size=18)
        )+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Hair style by Gender")



```


## crosstabs


```{r}
table(dts$`How do you currently keep your pubic hair?`, dts$Politics4L,dts$PartnerPolitics4L, dts$Gender3C)
```




```{r fig.width=20,fig.height=8}

dts<-data_per_participant %>% filter(Gender3C=="Female")

percents <- data.frame(
  table(dts$`How do you currently keep your pubic hair?`, dts$Politics4L,dts$PartnerPolitics4L, dts$Gender3C)/rep(table(dts$Politics4L,dts$PartnerPolitics4L,dts$Gender3C),each=4)
)
colnames(percents) <- c("Hair style","Politics", "Partner's Politics","Gender3C","Percent")

library(ggplot2)
library(ggthemes)
#install.packages("hrbrthemes") # NOTE: CRAN version is 0.8.0
library(hrbrthemes)
# devtools::install_github('datarootsio/artyfarty')
# library("artyfarty")
#https://towardsdatascience.com/themes-to-spice-up-visualizations-with-ggplot2-3e275038dafa

percents$Labels <- as.character(percents$`Hair style`)
percents$Labels[percents$Percent<0.1]<-""
ggplot(percents, aes(fill=`Hair style`, x=`Partner's Politics`,y=Percent)) + 
  geom_bar(position="fill", stat="identity")+scale_y_continuous(labels=scales::percent_format())+
  coord_flip()+
  #geom_text(aes(label = str_wrap(Labels,width=10)), hjust = 0,position = position_fill(vjust = 0)) +
  #theme_classic()+
  #theme_fivethirtyeight()+
  facet_wrap(~Politics,nrow=2)+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=22),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=22),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
        )+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Women's Hair style by politics and partner's politics")



```



```{r fig.width=20,fig.height=8}

dts<-data_per_participant %>% filter(Gender3C=="Female" & dts$Politics4L=="Mainstream liberal or left-wing")

percents <- data.frame(
  table(dts$`How do you currently keep your pubic hair?`, dts$PartnerPolitics4L)/rep(table(dts$PartnerPolitics4L),each=4)
)
colnames(percents) <- c("Hair style","Partner's Politics","Percent")

library(ggplot2)
library(ggthemes)
#install.packages("hrbrthemes") # NOTE: CRAN version is 0.8.0
library(hrbrthemes)
# devtools::install_github('datarootsio/artyfarty')
# library("artyfarty")
#https://towardsdatascience.com/themes-to-spice-up-visualizations-with-ggplot2-3e275038dafa

percents$Labels <- as.character(percents$`Hair style`)
percents$Labels[percents$Percent<0.1]<-""
ggplot(percents, aes(fill=`Hair style`, x=`Partner's Politics`,y=Percent)) + 
  geom_bar(position="fill", stat="identity")+scale_y_continuous(labels=scales::percent_format())+
  coord_flip()+
  #geom_text(aes(label = str_wrap(Labels,width=10)), hjust = 0,position = position_fill(vjust = 0)) +
  #theme_classic()+
  #theme_fivethirtyeight()+
  #facet_wrap(~Politics,nrow=2)+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=22),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=22),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
        )+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Women's Hair style by partner's politics (woman's own politics mainstream liberal")



```
