---
title: "Linear modeling"
output: html_notebook
---

This document breaks down the linear modeling to assess factors that seem to be important.

setup:

```{r}
source("utils.R")
raw_dataset <- get_raw_dataset()
```

```{r}

source("utils.R")

data_per_participant <- create_participant_data(raw_dataset)
data_per_participant_early <- create_participant_data(raw_dataset[1:430,])

```

# Descriptive stats

Graphs of stats taht we might wanna know for modeling below

```{r}
hist(data_per_participant$AgeGap[abs(data_per_participant$AgeGap)<30],breaks = -30:30)
```

# Sexual orientation data quality check


```{r}

data_per_participant$ConsecSet <- floor((1:nrow(data_per_participant))/200)*200
table(data_per_participant$HeteroRShip,data_per_participant$ConsecSet)
table(data_per_participant$SameSex,data_per_participant$ConsecSet)


```
Seems relatively constant throughout the set which is helpful.


```{r}
table(data_per_participant$SexualOrientation)
```

# from prior

# non-hetero relationships

```{r}



## non-hetero relationships
data_per_participant_nh <- data_per_participant[data_per_participant$HeteroRShip==FALSE,]
percents_nh <- data.frame(
  table(data_per_participant_nh$`How do you currently keep your pubic hair?`,data_per_participant_nh$Gender3C)/rep(table(data_per_participant_nh$Gender3C),each=4)
)

counts_nh <- data.frame(
  table(data_per_participant_nh$`How do you currently keep your pubic hair?`,data_per_participant_nh$Gender3C)#/rep(table(data_per_participant_nh$Gender),each=4)
)

colnames(counts_nh) <- c("Hair style","Gender3C","Count")


ggplot(counts_nh, aes(fill=`Hair style`, x=Gender3C,y=Count)) + 
  geom_bar(stat="identity")+#scale_y_continuous(labels=scales::percent_format())+
  coord_flip()+
  #theme_classic()+
  #theme_fivethirtyeight()+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",text = element_text(size = 18,face = "bold"))+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Hair style by Gender",subtitle="People in non-HeteroRShip relationships")


## same-sex relationships
data_per_participant_nh <- data_per_participant[data_per_participant$SameSex==TRUE,]

counts_nh <- data.frame(
  table(data_per_participant_nh$`How do you currently keep your pubic hair?`,data_per_participant_nh$Gender3C)#/rep(table(data_per_participant_nh$Gender),each=4)
)

colnames(counts_nh) <- c("Hair style","Gender3C","Count")


ggplot(counts_nh, aes(fill=`Hair style`, x=Gender3C,y=Count)) + 
  geom_bar(stat="identity")+#scale_y_continuous(labels=scales::percent_format())+
  coord_flip()+
  #theme_classic()+
  #theme_fivethirtyeight()+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",text = element_text(size = 18,face = "bold"))+
  scale_fill_brewer(palette = "YlOrRd")+
  #geom_text(aes(label=`Hair style`,y=Percent,x=Gender))+
  labs(title="Hair style by Gender",subtitle="People in same-sex relationships")

```
# same-sex vs. straight comparison 

This is based on relationship the person is in. not self-reported sexuality, which we only recorded late in the game.
```{r, fig.width=14,fig.height=7}

data_per_participant_sss <- data_per_participant[
  (data_per_participant$SameSex==TRUE | data_per_participant$HeteroRShip==TRUE) & 
    data_per_participant$Gender3C!="Non-binary" & 
    !is.na(data_per_participant$`How do you currently keep your pubic hair?`)
    ,]

data_per_participant_sss$Gender3C<-factor(data_per_participant_sss$Gender3C,c("Male","Female"))

counts_sss <- data.frame(
  table(data_per_participant_sss$`How do you currently keep your pubic hair?`,
        data_per_participant_sss$Gender3C,
        data_per_participant_sss$HeteroRShip)
)

colnames(counts_sss) <- c("Hair style","Gender3C","Straight","Count")

pc_sss <- data.frame(
  table(data_per_participant_sss$`How do you currently keep your pubic hair?`,
        data_per_participant_sss$Gender3C,
        data_per_participant_sss$HeteroRShip)/rep(table(data_per_participant_sss$Gender3C,data_per_participant_sss$HeteroRShip),each=4)
)
group_counts <- data.frame(table(
        data_per_participant_sss$Gender3C,
        data_per_participant_sss$HeteroRShip))

colnames(pc_sss) <- c("Hair style","Gender3C","Straight","Count")

pc_sss <- pc_sss%>% arrange(Gender3C,Straight)
labels <- c("Men (Male partner)","Men (Female partner)","Women (Female partner)","Women (Male partner)")
pc_sss$Label <- factor(
  rep(labels,each=4),
  labels)

men<-data_per_participant %>% filter(Gender3C=="Male" & (HeteroRShip | SameSex))
pc_sss$`Hair style`<-factor(pc_sss$`Hair style`,levels=rev(levels(pc_sss$`Hair style`)))
ggplot(pc_sss, aes(fill=`Hair style`, x=str_wrap(Label,16),y=Count)) + 
#ggplot(pc_sss, aes(fill=`Hair style`, x=interaction(Gender,Straight),y=Count)) + 
  geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent_format())+
 scale_x_discrete(name="")+
  coord_flip()+
  #theme_classic()+
  #theme_fivethirtyeight()+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",text = element_text(size = 18,face = "bold"))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=22),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=22),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
  )+
  scale_fill_brewer(palette = "YlOrRd")+
  labs(title="Hair style and Sexuality")
counts_sss

```
## Including non-binary participants

```{r, fig.width=12,fig.height=8}

data_per_participant_cleaned <- data_per_participant[
  #(data_per_participant$SameSex==TRUE | data_per_participant$HeteroRShip==TRUE) & 
    #data_per_participant$Gender3C!="Non-binary" & 
    !is.na(data_per_participant$`How do you currently keep your pubic hair?`)
    ,]

counts_crosstabs<-  table(data_per_participant_cleaned$`How do you currently keep your pubic hair?`,
        data_per_participant_cleaned$Gender3C,
        data_per_participant_cleaned$PartnerGender3C)

counts_nb <- data.frame(
  counts_crosstabs
)

colnames(counts_nb) <- c("Hair style","Gender3C","PartnerGender3C","Count")

pc_sss <- data.frame(
  counts_crosstabs/rep(table(data_per_participant_cleaned$Gender3C,data_per_participant_cleaned$PartnerGender3C),each=4)
)


colnames(pc_sss) <- c("Hair style","Gender3C","PartnerGender3C","Count")

#pc_sss <- pc_sss%>% arrange(desc(PartnerGender3C),desc(Gender3C))
pc_sss <- pc_sss%>% arrange(Gender3C,PartnerGender3C)

#labels<-str_wrap(paste0(pc_sss$Gender3C, " (",pc_sss$PartnerGender3C," partner)"),16)
#labels<-paste0(pc_sss$Gender3C, "\n(",pc_sss$PartnerGender3C," partner)")
labels<-paste0("...",pc_sss$PartnerGender3C," partner")

pc_sss$Label <- factor(labels,levels = rev(unique(labels)))

pc_sss$strip_labels<-paste0(pc_sss$Gender3C, " with...")
pc_sss$`Hair style`<-factor(pc_sss$`Hair style`,levels=rev(levels(pc_sss$`Hair style`)))
ggplot(pc_sss, aes(fill=`Hair style`, x=Label,y=Count)) + 
  geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent_format())+
 scale_x_discrete(name="")+
  coord_flip()+
  #theme_classic()+
  #theme_fivethirtyeight()+
  facet_wrap(strip_labels~.,scales = "free",ncol=1)+
  guides(fill=guide_legend(nrow=2,byrow=TRUE,reverse=TRUE))+
  theme(legend.position = "bottom",text = element_text(size = 16,face = "bold"))+
  theme(legend.position = "bottom",
        text = element_text(size = 16,face = "bold",color="#bd0026"),
        legend.text = element_text(size=16),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=16),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill="#000000"),
        strip.text = element_text(color="#ffffff",size=16)
  )+
  scale_fill_brewer(palette = "YlOrRd")+
  labs(title="Hair style and Sexuality")
counts_sss

```


## Repeating that but from the early data


```{r}

data_per_participant_sss <- data_per_participant_early[
  (data_per_participant_early$SameSex==TRUE | data_per_participant_early$HeteroRShip==TRUE) & 
    data_per_participant_early$Gender3C!="Non-binary" & 
    !is.na(data_per_participant_early$`How do you currently keep your pubic hair?`)
    ,]

data_per_participant_sss$Gender3C<-factor(data_per_participant_sss$Gender3C,c("Male","Female"))

counts_sss <- data.frame(
  table(data_per_participant_sss$`How do you currently keep your pubic hair?`,
        data_per_participant_sss$Gender3C,
        data_per_participant_sss$HeteroRShip)
)
colnames(counts_sss) <- c("Hair style","Gender3C","Straight","Count")

pc_sss <- data.frame(
  table(data_per_participant_sss$`How do you currently keep your pubic hair?`,
        data_per_participant_sss$Gender3C,
        data_per_participant_sss$HeteroRShip)/rep(table(data_per_participant_sss$Gender3C,data_per_participant_sss$HeteroRShip),each=4)
)

colnames(pc_sss) <- c("Hair style","Gender3C","Straight","Count")

pc_sss <- pc_sss%>% arrange(Gender3C,Straight)
labels <- c("Gay Men","Straight Men","Lesbian Women","Straight Women")
pc_sss$Label <- factor(
  rep(labels,each=4),
  labels)


ggplot(pc_sss, aes(fill=`Hair style`, x=Label,y=Count)) + 
#ggplot(pc_sss, aes(fill=`Hair style`, x=interaction(Gender,Straight),y=Count)) + 
  geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent_format())+
 scale_x_discrete(name="")+
  coord_flip()+
  #theme_classic()+
  #theme_fivethirtyeight()+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",text = element_text(size = 18,face = "bold"))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=22),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=22),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
  )+
  scale_fill_brewer(palette = "YlOrRd")+
  labs(title="Hair style and Sexuality",subtitle = "Early participants")


```

## Repeating that but from self-reported sexual oriengation



```{r}
# 
# data_per_participant_sss <- data_per_participant[
#   (data_per_participant$SameSex==TRUE | data_per_participant$HeteroRShip==TRUE) & 
#     data_per_participant$Gender3C!="Non-binary" & 
#     !is.na(data_per_participant$`How do you currently keep your pubic hair?`)
#     ,]
# 
# data_per_participant_sss$Gender3C<-factor(data_per_participant_sss$Gender3C,c("Male","Female"))
# 
# counts_sss <- data.frame(
#   table(data_per_participant_sss$`How do you currently keep your pubic hair?`,
#         data_per_participant_sss$Gender3C,
#         data_per_participant_sss$HeteroRShip)
# )
table(data_per_participant$Gender3C,data_per_participant$SexualOrientation6C)

data_per_participant_slgb<-data_per_participant %>% filter(
  SexualOrientation6C %in% c("Straight","Lesbian","Gay","Bisexual","Pansexual") & 
    (Gender3C!="Non-binary")
  )

pc_so <- data.frame(
  table(data_per_participant_slgb$`How do you currently keep your pubic hair?`,
        data_per_participant_slgb$Gender3C,
        data_per_participant_slgb$SexualOrientation6C)/rep(table(data_per_participant_slgb$Gender3C,data_per_participant_slgb$SexualOrientation6C),each=4)
)

colnames(pc_so) <- c("Hair style","Gender3C","Sexual Orientation","Count")

pc_so<- pc_so[is.nan(pc_so$Count)==FALSE,]
#pc_so<- pc_so[pc_so$Count>10,]
#pc_sss <- pc_sss%>% arrange(Gender3C,Straight)
#labels <- c("Gay Men","Straight Men","Lesbian Women","Straight Women")
# pc_sss$Label <- factor(
#   rep(labels,each=4),
#   labels)


ggplot(pc_so, aes(fill=`Hair style`, x=interaction(`Sexual Orientation`,Gender3C),y=Count)) + 
#ggplot(pc_sss, aes(fill=`Hair style`, x=interaction(Gender,Straight),y=Count)) + 
  geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent_format())+
 scale_x_discrete(name="")+
  coord_flip()+
  #theme_classic()+
  #theme_fivethirtyeight()+
  guides(fill=guide_legend(ncol=4,reverse=TRUE))+
  theme(legend.position = "bottom",text = element_text(size = 18,face = "bold"))+
  theme(legend.position = "bottom",
        text = element_text(size = 18,face = "bold",color="#bd0026"),
        legend.text = element_text(size=22),
        legend.background = element_rect(fill = "#ffffcc"),
        axis.text = element_text(color="#000000",size=22),
        plot.background = element_rect(fill = "#ffffcc"),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
  )+
  scale_fill_brewer(palette = "YlOrRd")+
  labs(title="Hair style and Sexuality")


```



